Paper_analyses

### 2021-12-08 Paper_Analyses_subj_obje_arousal.Rmd
Quick check on MFA and entropy for MI

```{r}
fviz_mfa_axes(res.mfa_agg_byval2)

>>>>

```{r}
fviz_mfa_axes(res.mfa_agg_byval2)
fviz_mfa_axes()

Mutual information

```{r}
install.packages("infotheo")
library(infotheo)

mutinformation(X, Y, method="emp")
?mutinformation
mutinformation(clustering_new_pre_PCA_2$arousal, clustering_new_pre_PCA_2$pup_basCor, 
               method="mm")

install.packages("entropy")

entropy::mi.plugin(clustering_new_pre_PCA_2[,c(3,6)])
```
